---
title: "02.04.01-Quiz Notebook"
output:
  html_document: default
  html_notebook: default
  pdf_document: default
---

Import the .R files to the environment;
```{r}
source("pollutantmean.R")
source("complete.R")
source("corr.R")
```

### Question 1
What value is returned by the following call to `pollutantmean()`? You should round your output to 3 digits.
```
pollutantmean("specdata", "sulfate", 1:10)
```
```{r Question 1, echo=TRUE}
pollutantmean("specdata", "sulfate", 1:10)
```

### Question 2
What value is returned by the following call to `pollutantmean()`? You should round your output to 3 digits.
```
pollutantmean("specdata", "nitrate", 70:72)
```
```{r Question 2, echo=TRUE}
pollutantmean("specdata", "nitrate", 70:72)
```

### Question 3
What value is returned by the following call to `pollutantmean()`? You should round your output to 3 digits.
```
pollutantmean("specdata", "sulfate", 34)
```
```{r Question 3, echo=TRUE}
pollutantmean("specdata", "sulfate", 34)
```

### Question 4
What value is returned by the following call to `pollutantmean()`? You should round your output to 3 digits.
```
pollutantmean("specdata", "nitrate")
```
```{r Question 4, echo=TRUE}
pollutantmean("specdata", "nitrate")
```

### Question 5
What value is printed at end of the following code?
```
cc <- complete("specdata", c(6, 10, 20, 34, 100, 200, 310))
print(cc$nobs)
```
```{r Question 5, echo=TRUE}
cc <- complete("specdata", c(6, 10, 20, 34, 100, 200, 310))
print(cc$nobs)
```

### Question 6
What value is printed at end of the following code?
```
cc <- complete("specdata", 54)
print(cc$nobs)
```
```{r Question 6, echo=TRUE}
cc <- complete("specdata", 54)
print(cc$nobs)
```

### Question 7
What value is printed at end of the following code?
```
set.seed(42)
cc <- complete("specdata", 332:1)
use <- sample(332, 10)
print(cc[use, "nobs"])
```
```{r Question 7, echo=TRUE}
set.seed(42)
cc <- complete("specdata", 332:1)
use <- sample(332, 10)
print(cc[use, "nobs"])
```

### Question 8
What value is printed at end of the following code?
```
cr <- corr("specdata")                
cr <- sort(cr)                
set.seed(868)                
out <- round(cr[sample(length(cr), 5)], 4)
print(out)
```
```{r Question 8, echo=TRUE}
cr <- corr("specdata")                
cr <- sort(cr)                
set.seed(868)                
out <- round(cr[sample(length(cr), 5)], 4)
print(out)
```

### Question 9
What value is printed at end of the following code?
```
cr <- corr("specdata", 129)                
cr <- sort(cr)                
n <- length(cr)                
set.seed(197)                
out <- c(n, round(cr[sample(n, 5)], 4))
print(out)
```
```{r Question 9, echo=TRUE}
cr <- corr("specdata", 129)                
cr <- sort(cr)                
n <- length(cr)                
set.seed(197)                
out <- c(n, round(cr[sample(n, 5)], 4))
print(out)
```

### Question 10
What value is printed at end of the following code?
```
cr <- corr("specdata", 2000)                
n <- length(cr)                
cr <- corr("specdata", 1000)                
cr <- sort(cr)
print(c(n, round(cr, 4)))
```
```{r Question 10, echo=TRUE}
cr <- corr("specdata", 2000)                
n <- length(cr)                
cr <- corr("specdata", 1000)                
cr <- sort(cr)
print(c(n, round(cr, 4)))
```



